```{r}
library(XML)
# install.packages('dplyr')
library(dplyr)
library(ggplot2)
library(readr)
library(forecast)
library(readxl)
library(DIMORA)
library(cowplot)
library(gbm)
library(tree)


```

## Italy data

```{r}
it_cinema <- read.csv("italy_data.csv")
it_cinema
```
Some cleaning

```{r}
it_cinema$Week <- as.numeric(as.character(it_cinema$Week))
it_cinema$Week <- as.numeric(as.character(it_cinema$Week))
it_cinema$Date <- with(it_cinema, as.Date(paste0(it_cinema$Year, "-01-01"), format="%Y-%m-%d", origin="1970-01-01") +
                                               as.difftime(it_cinema$Week, unit="weeks"))
it_cinema$Overall.Gross <- parse_number(it_cinema$Overall.Gross)

it_cinema <- it_cinema[order(as.Date(it_cinema$Date)),]

```

Plot

```{r,fig.width = 8}
theme_update(plot.title = element_text(hjust = 0.5))
ggplot( data = it_cinema, aes( Date, Overall.Gross )) + geom_line() + 
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  ggtitle("Weekly income data") 

```

## Covid time definition

```{r}
it_cinema_precovid = it_cinema[which(it_cinema$Date < "2020-03-10"),]
it_cinema_covid = it_cinema[which(it_cinema$Date > "2020-03-11"),]
it_cinema_postcovid = it_cinema[which(it_cinema$Date > "2021-04-01"),]

```

## Full time series (with covid)



```{r}
it_cinema_monthly <-it_cinema %>% 
    group_by(month = lubridate::floor_date(Date, "month")) %>%
    summarize(Montly.gross = sum(Overall.Gross))

# ggplot( data = it_cinema_monthly, aes( month, Montly.gross )) + geom_line() +
#     scale_x_date(date_breaks = "2 years", date_labels = "%Y")


```
### ACF and PACF

```{r}
acf(it_cinema_monthly$Montly.gross , lag.max = 50)
pacf(it_cinema_monthly$Montly.gross , lag.max = 50)

```


### Linear regression

```{r}
# fit1 <- lm(it_cinema$Overall.Gross ~ it_cinema$Date)
# summary(fit1)
# 
# resfit1<- residuals(fit1)
# plot(resfit1,xlab="Time", ylab="residuals" )
# 
# ggplot( ) +
#   geom_line(data = it_cinema, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema, aes(Date, fitted(fit1)), color="red")
```

### Now with seasonality and trend
```{r}

# #data transformed as time series
# it_cinema.ts<-ts(it_cinema$Overall.Gross, frequency=52)
# 
# #Model with trend and seasonality
# fit2 <- tslm(it_cinema.ts~ trend+season)
# summary(fit2)
# 
# #check the residuals
# res2 <- residuals(fit2)
# plot(res2)
# 
# 
# 
# ggplot( ) +
#   geom_line(data = it_cinema, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema, aes(Date, fitted(fit2)), color="red")
```
### Loess

```{r,fig.width = 8}
lo1 <- loess.smooth(it_cinema$Date,it_cinema$Overall.Gross,span=0.1) 
ggplot( ) +
  geom_line(data = it_cinema, aes( Date, Overall.Gross, color="Values")) +
  geom_line(data = data.frame(lo1), aes(lo1$x, lo1$y, color="Loess"))+
    scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
    ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
    scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Loess" = "red")) +
  ggtitle("Loess smoothing")


```


### Arima

```{r}
# cinema_diff <- diff(it_cinema$Overall.Gross,lag=1)
# ggtsdisplay(cinema_diff)
```


```{r}
# auto.arima<- auto.arima(it_cinema$Overall.Gross)
# ggplot( ) +
#   geom_line(data = it_cinema, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema, aes(Date, fitted(auto.arima)), color="red")
# 
# auto.arima
```


## Pre-covid 


```{r fig.width=8}
# it_cinema_full = it_cinema
ggplot( data = it_cinema_precovid, aes( Date, Overall.Gross )) + geom_line() + 
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  ggtitle("Weekly income data (pre Covid)") 
```

### Some EDA

Let's see what happens in 2009 and 2010



```{r fig.width=7}
ggplot( data = it_cinema_precovid[which(it_cinema_precovid$Year == 2009 | it_cinema_precovid$Year == 2010),], aes( Date, Overall.Gross )) + 
  geom_line() + 
  geom_point(size=1) + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b") +
  ylab("Income (millions $)") +
  xlab("Month") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  ggtitle("Weekly income data (between years 2009 and 2010)") 


```


```{r}
ggplot( data = it_cinema_precovid[which(it_cinema_precovid$Date >= "2009-12-20" & it_cinema_precovid$Date <= "2010-01-22"),], aes( Date, Overall.Gross )) + 
  geom_line() + 
  scale_x_date(date_breaks = "1 day", date_labels = "%d") +
  geom_point(size=2) + 
  ylab("Income (millions $)") +
  xlab("Month") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  ggtitle("Weekly income data (zoom in 2010)") 


```

tabella di questo: https://www.boxofficemojo.com/weekend/2009W52/?area=IT&ref_=bo_wey_table_2 (Natale a Beverly Hills)

### Comulated distribution of gross per week

```{r}
it_cinema_week <-it_cinema_precovid %>% 
    group_by(Week) %>%
    summarize(Weekly.mean.gross = mean(Overall.Gross))

# it_cinema_week

ggplot(it_cinema_week, aes(x=Week, y=Weekly.mean.gross)) + geom_bar(stat="identity", width=0.5) +
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_continuous(breaks = seq(1,52,3) ) +
  ggtitle("Weekly income data") 

```

### Trends for periods

Cumulated gross for periods (christmas, autumn, summer) to see how they trend over the years
 
```{r}
christmas <- it_cinema_precovid[which(it_cinema_precovid$Week >= 48 | it_cinema_precovid$Week <= 5),]
christmas <- christmas %>%
    group_by(Year) %>%
    summarize(Overall.Gross = sum(Overall.Gross))

autumn <- it_cinema_precovid[which(it_cinema_precovid$Week >= 39 & it_cinema_precovid$Week <= 48),]
autumn <- autumn %>%
    group_by(Year) %>%
    summarize(Overall.Gross = sum(Overall.Gross))

summer <- it_cinema_precovid[which(it_cinema_precovid$Week >= 23 & it_cinema_precovid$Week <= 38),]
summer <- summer %>%
    group_by(Year) %>%
    summarize(Overall.Gross = sum(Overall.Gross))

```

```{r fig.width=8}

christmas_plot <- ggplot( ) + 
  geom_line(data = christmas, aes( Year, Overall.Gross ), color="blue") +
  geom_point(data = christmas, aes( Year, Overall.Gross ), color="blue") +
  scale_x_continuous(breaks = round(seq(min(autumn$Year), max(autumn$Year), by = 2),1)) +
  scale_y_continuous(labels=function(x)x/1000000) +
  ylab("Income (millions $)")


autumn_plot <- ggplot( ) + 
  geom_line(data = autumn, aes( Year, Overall.Gross ), color="green") +
  geom_point(data = autumn, aes( Year, Overall.Gross ), color="green") +
  scale_x_continuous(breaks = round(seq(min(autumn$Year), max(autumn$Year), by = 2),1))+
  scale_y_continuous(labels=function(x)x/1000000)+
  ylab("Income (millions $)")

summer_plot <- ggplot( ) + 
  geom_line(data = summer, aes( Year, Overall.Gross ), color="red") +
  geom_point(data = summer, aes( Year, Overall.Gross ), color="red") +
  scale_x_continuous(breaks = round(seq(min(autumn$Year), max(autumn$Year), by = 2),1))+
  scale_y_continuous(labels=function(x)x/1000000)+
  ylab("Income (millions $)")


plot_grid(christmas_plot, autumn_plot, summer_plot, labels = c("Christmas","Autumn","Summer"),label_size = 12, hjust = -2.3, vjust = 1)
```
### Bass model

```{r}
bm_GC<-BM(it_cinema_precovid$Overall.Gross,display = T,
          prelimestimates = c(sum(it_cinema_precovid$Overall.Gross) + 100, 0.001, 0.1),)
summary(bm_GC)

```


```{r,fig.width = 8}
dates <- c(it_cinema_precovid$Date,seq(as.Date("2020-03-01"), as.Date("2023-03-01"), "week"))
pred_bmGC<- predict(bm_GC, newx=c(1:length(dates)))
pred.instGC<- make.instantaneous(pred_bmGC)
pred_bm <- data.frame(cbind(dates,pred.instGC))
pred_bm$dates <- dates
pred_bm$pred.instGC <- pred.instGC
ggplot( ) +
  geom_line(data = it_cinema_precovid, aes( Date, Overall.Gross, color="Values")) +
  geom_line(data = pred_bm, aes( dates, pred.instGC, color="Prediction")) +
  geom_line(data = it_cinema_covid, aes(Date, Overall.Gross, color="Observed"), linetype="dashed") +
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red",
                              "Observed" = "blue"))+
  ggtitle("Bass Model for pre covid data")

```
### Linear regression

```{r}
# fit1 <- lm(it_cinema_precovid$Overall.Gross ~ it_cinema_precovid$Date)
# summary(fit1)
# 
# resfit1<- residuals(fit1)
# plot(resfit1,xlab="Time", ylab="residuals" )
# 
# ggplot( ) +
#   geom_line(data = it_cinema_precovid, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema_precovid, aes(Date, fitted(fit1)), color="red")
```
### Now with seasonality and trend
```{r,fig.width = 8}

#data transformed as time series
it_cinema_precovid.ts<-ts(it_cinema_precovid$Overall.Gross, frequency=52)

#Model with trend and seasonality
fit2 <- tslm(it_cinema_precovid.ts~ trend+season)
summary(fit2)

#check the residuals
res2 <- residuals(fit2)
plot(res2)

# fit1 <- lm(it_cinema$Overall.Gross ~ it_cinema$Date)
# summary(fit1)

for1<- forecast(fit2,level=95,h=141)
low <- for1$lower[1:length(for1$lower)]
up <- for1$upper[1:length(for1$upper)]
mean <- for1$mean



ggplot( ) +
  geom_line(data = it_cinema_precovid, aes( Date, Overall.Gross)) +
  geom_line(data = it_cinema_precovid, aes(Date, fitted(fit2), color="Prediction")) +
  geom_smooth(data = it_cinema_covid, aes(x=Date, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
  geom_line(data = it_cinema_covid, aes(Date, Overall.Gross, color="Observed"), linetype="dashed") +
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red",
                              "Observed" = "blue")) +
  ggtitle("Linear regression for pre covid data")

```


### Arima

```{r}
cinema_diff <- diff(it_cinema_precovid$Overall.Gross,lag=1)
ggtsdisplay(cinema_diff)
```
```{r}
arima<- Arima(it_cinema_precovid$Overall.Gross,order=c(3,1,1), seasonal=list(order=c(0,1,1), period = 52))
for1<- forecast(arima,level=95,h=length(it_cinema_covid$Overall.Gross))
low <- for1$lower[1:length(for1$lower)]
up <- for1$upper[1:length(for1$upper)]
mean <- for1$mean

```


```{r,fig.width = 8}
# arima<- Arima(it_cinema_precovid$Overall.Gross,order=c(3,1,1), seasonal=list(order=c(1,1,1), period = 52))
ggplot( ) +
  geom_line(data = it_cinema_precovid, aes( Date, Overall.Gross, color="Values")) +
  geom_line(data = it_cinema_precovid, aes(Date, fitted(arima), color="Prediction")) +
  geom_smooth(data = it_cinema_covid, aes(x=Date, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
  geom_line(data = it_cinema_covid, aes(Date, Overall.Gross, color="Observed"), linetype="dashed") +
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red",
                              "Observed" = "blue")) +
  ggtitle("ARIMA modeling for pre covid data")


arima
checkresiduals(arima)
```



```{r}
# arima<- auto.arima(myts,seasonal=TRUE)
# 
# ggplot( ) +
#   geom_line(data = it_cinema_precovid, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema_precovid, aes(Date, fitted(arima)), color="red")
# 
# arima
# checkresiduals(arima)
```






## Productions nationality


```{r}
prods <- read.csv("productions.csv")

prods$Date <- with(prods, as.Date(paste0(prods$Year, "-01-01"), format="%Y-%m-%d", origin="1970-01-01") +
                                               as.difftime(prods$Week, unit="weeks"))
prods
```
Italian productions in black, foreign in red

```{r fig.width=7}
# ggplot( ) + 
#   geom_line(data = prods, aes( Date, IT_movies ,color="Italian movies")) +
#   geom_line(data = prods, aes( Date, foreign_movies,color="Foreign movies")) +
#   ylab("Number of movies aired") +
#   scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
#   scale_color_manual(name  ="Legend",
#                      values=c("Italian movies" = "springgreen1",
#                               "Foreign movies" = "orangered1")) 

```


## Netflix competition

```{r}
it_netflix <- read.csv("italy_netflix.csv",sep=";")
it_netflix$date <- as.Date(it_netflix$date, format="%d/%m/%Y")
```

```{r}
it_cinema_monthly$Montly.access = it_cinema_monthly$Montly.gross/7
it_cinema_monthly
```

```{r,fig.width = 7}
ggplot( ) +
  geom_line(data = it_cinema_monthly, aes( month, Montly.access, color="Cinema access")) + 
  geom_point(data = it_cinema_monthly, aes( month, Montly.access, color="Cinema access"),size=1.2) +
  geom_line(data = it_netflix, aes( date, n_access , color="Netflix access")) + 
  geom_point(data = it_netflix, aes( date, n_access , color="Netflix access"),size=1.2) +
  ylab("Number of movies aired") +
  xlab("Date") +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  ylab("Accesses (millions)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Cinema access" = "black",
                              "Netflix access" = "red")) +
  ggtitle("Comparison between monthly cinema and Netflix accesses")


```

```{r}
ucrcdNR<- UCRCD(it_cinema_monthly$Montly.access,it_netflix$n_access, display=T)
summary(ucrcdNR)

```


```{r}
dates <- c(it_cinema_precovid$Date,seq(as.Date("2020-03-01"), as.Date("2023-03-01"), "month"))

predUCRCD_cinema <- make.instantaneous(ucrcdNR$fitted[[1]])
predUCRCD_netflix <- make.instantaneous(ucrcdNR$fitted[[2]])
ggplot( ) +
  geom_line(data = it_cinema_monthly, aes( month, Montly.access, color="Cinema observ"),linetype="dashed") +
  geom_point(data = it_cinema_monthly, aes( month, Montly.access, color="Cinema observ"),size=1) +
  geom_line(data = it_cinema_monthly, aes( month, predUCRCD_cinema, color="Cinema BM")) +
  geom_line(data = it_netflix, aes(date, n_access , color="Netflix observ"), linetype="dashed") +
  geom_point(data = it_netflix, aes(date, n_access , color="Netflix observ"), linetype="dashed",size=1) +
  geom_line(data = it_netflix, aes(date, predUCRCD_netflix , color="Netflix BM")) +
  ylab("Number of access") +
  xlab("Date") +
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Cinema observ" = "red",
                              "Cinema BM" = "red",
                              "Netflix observ" = "blue",
                              "Netflix BM" = "blue"))+
  ggtitle("Bass Model with competition between cinema and Netflix accesses")

```


## Covid



```{r}
it_cinema_monthly <-it_cinema_covid %>% 
    group_by(month = lubridate::floor_date(Date, "month")) %>%
    summarize(Montly.gross = sum(Overall.Gross))

# ggplot( data = it_cinema_monthly, aes( month, Montly.gross )) + geom_line() 

```
### Bass Model

```{r}
bm_GC<-BM(it_cinema_covid$Overall.Gross,display = T,
          prelimestimates = c(sum(it_cinema_covid$Overall.Gross) + 100, 0.001, 0.01),)
summary(bm_GC)

dates <- it_cinema_covid$Date
pred_bmGC<- predict(bm_GC, newx=c(1:length(dates)))
pred.instGC<- make.instantaneous(pred_bmGC)
pred_bm <- data.frame(cbind(dates,pred.instGC))
pred_bm$dates <- dates
pred_bm$pred.instGC <- pred.instGC
ggplot( ) +
  geom_line(data = it_cinema_covid, aes( Date, Overall.Gross, color="Values")) +
  geom_point(data = it_cinema_covid, aes( Date, Overall.Gross, color="Values"),size=1.2) +
  geom_line(data = pred_bm, aes( dates, pred.instGC, color="Bass Model"))+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Bass Model" = "red"))+
  ggtitle("Bass Model on covid data")
```

### Bass Model with Shock

```{r}
bm_GC<-GBM(it_cinema_covid$Overall.Gross, display = T,
          shock="rett", nshock = 2,
          prelimestimates = c(sum(it_cinema_covid$Overall.Gross) + 100, 0.01, 0.01,
          0, 15, -0.8,
          15, 30, +1),
          # shock="rett", nshock = 3,
          # prelimestimates = c(sum(it_cinema$Overall.Gross) + 100, 0.01, 0.01,
          #                     1, 15, -1,
          #                     10, 20, +0.5,
          #                     20, 31, -0.5)


)
summary(bm_GC)

dates <- c(it_cinema_covid$Date,seq(as.Date("2022-12-03"), as.Date("2023-07-01"), "week"))
pred_bmGC<- predict(bm_GC, newx=c(1:length(dates)))
pred.instGC<- make.instantaneous(pred_bmGC)
pred_bm <- data.frame(cbind(dates,pred.instGC))
pred_bm$dates <- dates
pred_bm$pred.instGC <- pred.instGC

ggplot( ) +
  geom_line(data = it_cinema_covid, aes( Date, Overall.Gross, color="Values")) +
  geom_point(data = it_cinema_covid, aes( Date, Overall.Gross, color="Values"),size=1.2)+
  geom_line(data = pred_bm, aes( dates, pred.instGC, color="Bass Model"))+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Bass Model" = "red"))+
  ggtitle("Bass Model on covid data, 2 shocks")


```


## Post covid

```{r}
future <- seq(as.Date("2022-12-03"), as.Date("2023-07-01"), by = "week")
length(future)
future_pred <- data.frame(future,future)
```

### Bass Model

```{r}


bm_GC<-BM(it_cinema_postcovid$Overall.Gross,display = T,
          prelimestimates = c(sum(it_cinema_postcovid$Overall.Gross) + 100, 0.01, 0.01),)
summary(bm_GC)

dates <- c(it_cinema_postcovid$Date,seq(as.Date("2022-12-03"), as.Date("2023-07-01"), "week"))
pred_bmGC<- predict(bm_GC, newx=c(1:length(dates)))
pred.instGC<- make.instantaneous(pred_bmGC)
pred_bm <- data.frame(cbind(dates,pred.instGC))
pred_bm$dates <- dates
pred_bm$pred.instGC <- pred.instGC

ggplot( ) +
  geom_line(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values")) +
  geom_point(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values"),size=1.2)+
  geom_line(data = pred_bm, aes( dates, pred.instGC, color="Bass Model"))+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Bass Model" = "red")) +
  ggtitle("Bass Model on post covid data")


```
```{r}
it_cinema_postcovid
```

### Linear regression
```{r}
# fit1 <- lm(it_cinema_postcovid$Overall.Gross ~ it_cinema_postcovid$Date)
# summary(fit1)
# 
# resfit1<- residuals(fit1)
# plot(resfit1,xlab="Time", ylab="residuals" )
# 
# ggplot( ) +
#   geom_line(data = it_cinema_postcovid, aes( Date, Overall.Gross)) +
#   geom_line(data = it_cinema_postcovid, aes(Date, fitted(fit1)), color="red")
```
### Now with seasonality and trend



```{r}

#data transformed as time series
it_cinema_postcovid.ts<-ts(it_cinema_postcovid$Overall.Gross, frequency=52)

#Model with trend and seasonality
fit2 <- tslm(it_cinema_postcovid.ts~ trend+season)
summary(fit2)

#check the residuals
res2 <- residuals(fit2)
plot(res2)

# fit1 <- lm(it_cinema$Overall.Gross ~ it_cinema$Date)
# summary(fit1)

for1<- forecast(fit2,level=95,h=31)
low <- for1$lower[1:length(for1$lower)]
up <- for1$upper[1:length(for1$upper)]
mean <- for1$mean


ggplot( ) +
  geom_line(data = it_cinema_postcovid, aes( Date, Overall.Gross)) +
  geom_point(data = it_cinema_postcovid, aes( Date, Overall.Gross),size=1.2)+
  geom_line(data = it_cinema_postcovid, aes(Date, fitted(fit2), color="Prediction")) +
  geom_point(data = it_cinema_postcovid, aes(Date, fitted(fit2), color="Prediction"),size=1.2)+
  geom_smooth(data = future_pred, aes(x=future, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
  geom_point(data = future_pred, aes(x=future, y=mean, color="Prediction"),size=1.2)+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red")) +
  ggtitle("Forecasting with Linear Regression model")
```

### Arima

```{r}
cinema_diff <- diff(it_cinema_postcovid$Overall.Gross,lag=1)
ggtsdisplay(cinema_diff)
```

```{r}
arima<- Arima(it_cinema_postcovid$Overall.Gross,
              order=c(2,1,1),seasonal = list(order=c(0,1,1),period=12))
ggplot( ) +
  geom_line(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values")) +
  geom_point(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values"),size=1.2)+
  geom_line(data = it_cinema_postcovid, aes(Date, fitted(arima), color="Prediction")) +
  geom_point(data = it_cinema_postcovid, aes(Date, fitted(arima), color="Prediction"),size=1.2)+
  geom_smooth(data = future_pred, aes(x=future, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
  geom_point(data = future_pred, aes(x=future, y=mean, color="Prediction"),size=1.2)+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red"))+
  ggtitle("Forecasting with ARIMA model")

arima
checkresiduals(arima)
```
```{r}
arima<- auto.arima(it_cinema_postcovid$Overall.Gross)
ggplot( ) +
  geom_line(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values")) +
  geom_point(data = it_cinema_postcovid, aes( Date, Overall.Gross, color="Values"),size=1.2)+
  geom_line(data = it_cinema_postcovid, aes(Date, fitted(arima), color="Prediction")) +
  geom_point(data = it_cinema_postcovid, aes(Date, fitted(arima), color="Prediction"),size=1.2)+
  geom_smooth(data = future_pred, aes(x=future, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
  geom_point(data = future_pred, aes(x=future, y=mean, color="Prediction"),size=1.2)+
  ylab("Income (millions $)") + 
  scale_y_continuous(labels=function(x)x/1000000) + 
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Values" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red"))+
  ggtitle("Forecasting with ARIMA model")

arima
checkresiduals(arima)
```


## Multiple predictors 


```{r}
netflix_access <- c(rep(0,96),it_netflix$n_access)
```

```{r}
it_cinema_monthly <-it_cinema %>% 
    group_by(month = lubridate::floor_date(Date, "month")) %>%
    summarize(Montly.gross = sum(Overall.Gross))

```

```{r}
prods_monthly <-prods %>% 
    group_by(month = lubridate::floor_date(Date, "month")) %>%
    summarize(IT_movies = sum(IT_movies),foreign_movies = sum(foreign_movies) )

# ggplot( ) + 
#   geom_line(data = prods_monthly, aes( month, IT_movies )) +
#   geom_line(data = prods_monthly, aes( month, foreign_movies ),color="red") 

ggplot( ) + 
  geom_line(data = prods_monthly, aes( month, IT_movies ,color="Italian movies")) +
  geom_point(data = prods_monthly, aes( month, IT_movies ,color="Italian movies")) +
  geom_line(data = prods_monthly, aes( month, foreign_movies,color="Foreign movies")) +
  geom_point(data = prods_monthly, aes( month, foreign_movies,color="Foreign movies")) +
  ylab("Number of movies aired") +
  xlab("Date") +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Italian movies" = "springgreen1",
                              "Foreign movies" = "orangered1")) +
  ggtitle("Number of italian and foreign movies aired monthly")
```
```{r}
prods_monthly$perc <- prods_monthly$IT_movies/prods_monthly$foreign_movies
# prods_monthly <- na.omit(prods_monthly)
prods_monthly <- do.call(data.frame,lapply(prods_monthly, function(x) replace(x, is.infinite(x),NA)))
prods_monthly[is.na(prods_monthly)] <- 1
prods_monthly
```




```{r}
cinema_data <- merge(x = it_cinema_monthly, y = prods_monthly, by = "month", all = TRUE)
cinema_data$netflix_access <- netflix_access
cinema_data <- na.omit(cinema_data)
cinema_data
```

```{r}
# ggplot( ) + 
#   geom_line(data = cinema_data, aes( month, Montly.gross/40000000 )) +
#   geom_line(data = cinema_data, aes( month, perc ),color="red") +
#   geom_line(data = cinema_data, aes( month, netflix_access/6000000 ), color="blue")


```
### Linear Regression
```{r}
future <- seq(as.Date("2022-12-03"), as.Date("2023-07-01"), by = "month")
length(future)
future_pred <- data.frame(future,future)

```

```{r}
fit3 <- lm(cinema_data$Montly.gross ~ cinema_data$perc + cinema_data$netflix_access)
summary(fit3)

resfit1<- residuals(fit3)
plot(resfit1,xlab="Time", ylab="residuals" )


# 
# ggplot( ) +
#   geom_line(data = cinema_data, aes( Date, Overall.Gross)) +
#   geom_point(data = cinema_data, aes( Date, Overall.Gross),size=1.2)+
#   geom_line(data = cinema_data, aes(Date, fitted(fit2), color="Prediction")) +
#   geom_point(data = it_cinema_postcovid, aes(Date, fitted(fit2), color="Prediction"),size=1.2)+
#   geom_smooth(data = future_pred, aes(x=future, y=mean, ymax=up, ymin=low, color="Prediction"),stat='identity',size=0) +
#   geom_point(data = future_pred, aes(x=future, y=mean, color="Prediction"),size=1.2)+
#   ylab("Income (millions $)") + 
#   scale_y_continuous(labels=function(x)x/1000000) +
#   scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
#   scale_color_manual(name  ="Legend",
#                      values=c("Values" = "black",
#                               "Prediction" = "red",
#                               "Prediction" = "red")) +
#   ggtitle("Forecasting with Linear Regression model")


ggplot( ) +
  geom_line(data = cinema_data, aes( month, Montly.gross, color="Observed")) +
  geom_point(data = cinema_data, aes( month, Montly.gross),size=1) +
  geom_line(data = cinema_data, aes(month, fitted(fit3), color="Prediction")) +
  geom_point(data = cinema_data, aes(month, fitted(fit3), color="Prediction"),size=1) +
  ylab("Accesses (millions)") + 
  xlab("Date") +
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Observed" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red")) +
  ggtitle("Forecasting with Linear Regression model")


```
### GBM

```{r}
fit4 <- gbm(cinema_data$Montly.gross ~ cinema_data$perc + cinema_data$netflix_access,train.fraction = 0.99,n.trees=500)
summary(fit4)

Yhat <- predict(fit4, n.trees=500, newdata = data.frame(cinema_data$perc,  cinema_data$netflix_access))
ggplot( ) +
  geom_line(data = cinema_data, aes( month, Montly.gross, color="Observed")) +
  geom_point(data = cinema_data, aes( month, Montly.gross),size=1) +
  geom_line(data = cinema_data, aes(month, Yhat, color="Prediction")) +
  geom_point(data = cinema_data, aes(month, Yhat, color="Prediction"),size=1) +
  ylab("Accesses (millions)") + 
  xlab("Date") +
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Observed" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red")) +
  ggtitle("Forecasting with Gradient Boosting")


```

### Arima
```{r}

armax1<- Arima(cinema_data$Montly.gross, xreg=cbind(cinema_data$perc,cinema_data$netflix_access),
               order=c(2,1,1), seasonal=list(order=c(0,1,1), period =12))
res1<- residuals(armax1)

Yhat <- predict(fit4, n.trees=500, newdata = data.frame(cinema_data$perc,  cinema_data$netflix_access))
ggplot( ) +
  geom_line(data = cinema_data, aes( month, Montly.gross, color="Observed")) +
  geom_point(data = cinema_data, aes( month, Montly.gross),size=1) +
  geom_line(data = cinema_data, aes(month, fitted(armax1), color="Prediction")) +
  geom_point(data = cinema_data, aes(month, fitted(armax1), color="Prediction"),size=1) +
  ylab("Accesses (millions)") + 
  xlab("Date") +
  scale_y_continuous(labels=function(x)x/1000000) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  scale_color_manual(name  ="Legend",
                     values=c("Observed" = "black",
                              "Prediction" = "red",
                              "Prediction" = "red")) +
  ggtitle("Forecasting with ARIMA")

checkresiduals(cinema_diff)

```



